Summary Tables

### 2020-10-27 summary_tables.Rmd

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 98.1|72.3|2.9 |
| bicycle | 0.5|0.3|0.5 |
| car | 1.0|9.0|17.1 |
| motorcycle | 0.0|0.0|0.0 |
| bus | 0.0|15.0|64.4 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 62.2|7.2|3.0 |
| bicycle | 0.7|0.9|0.3 |
| car | 21.0|42.9|28.7 |
| motorcycle | 1.3|2.9|3.8 |
| bus | 13.3|39.2|32.7 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 84.4|10.1|0.9 |
| bicycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.7|24.7|32.7 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 74.9|23.0|1.0 |
| bicycle | 2.3|9.8|1.1 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|25.0 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 88.4|23.2|0.3 |
| bicycle | 3.5|8.7|2.3 |
| car | 7.2|45.5|35.5 |
| motorcycle | 0.1|1.4|1.4 |
| bus | 0.3|10.1|29.6 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 91.7|34.7|0.6 |
| bicycle | 0.4|3.5|1.0 |
| car | 7.2|38.4|39.5 |
| motorcycle | 0.2|6.3|7.4 |
| bus | 0.1|4.5|38.4 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 96.5|33.8|0.2 |
| bicycle | 2.4|8.3|1.2 |
| car | 0.5|24.8|25.7 |
| motorcycle | 0.0|1.8|1.5 |
| bus | 0.5|27.7|50.1 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.3|37.6|0.3 |
| bicycle | 0.8|7.4|1.2 |
| car | 2.4|24.9|29.6 |
| motorcycle | 0.0|3.1|1.9 |
| bus | 0.3|18.8|47.1 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 90.0|27.3|2.4 |
| bicycle | 4.5|15.1|4.2 |
| car | 1.4|13.3|18.7 |
| motorcycle | 0.4|5.6|7.2 |
| bus | 3.2|34.1|62.9 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 88.5|23.3|2.0 |
| bicycle | 0.0|0.4|0.3 |
| car | 9.4|46.1|47.3 |
| motorcycle | 0.0|0.3|0.6 |
| bus | 2.0|27.5|36.5 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 80.6|18.3|0.1 |
| bicycle | 3.9|7.2|2.0 |
| car | 0.6|2.3|2.4 |
| motorcycle | 9.5|23.8|25.0 |
| bus | 1.2|27.5|56.0 |

>>>>

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 98.5|0.0|0.0 |
| cycle | 0.5|1.5|0.4 |
| car | 0.8|29.8|14.4 |
| motorcycle | 0.0|0.1|1.0 |
| bus | 0.0|60.0|74.0 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 75.0|23.1|1.0 |
| cycle | 2.3|9.8|1.2 |
| car | 1.0|4.3|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|24.9 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 91.7|36.7|0.6 |
| cycle | 0.4|3.7|1.0 |
| car | 7.5|47.2|49.9 |
| motorcycle | 0.2|6.7|7.2 |
| bus | 0.1|4.8|37.5 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 90.0|26.8|2.3 |
| cycle | 4.5|14.8|4.1 |
| car | 1.5|15.0|21.0 |
| motorcycle | 0.4|5.5|6.9 |
| bus | 3.1|33.5|61.0 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 96.6|34.2|0.1 |
| cycle | 2.3|8.3|1.0 |
| car | 0.5|24.4|21.8 |
| motorcycle | 0.0|1.9|1.2 |
| bus | 0.6|27.8|48.2 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 88.5|23.3|2.0 |
| cycle | 0.0|0.4|0.3 |
| car | 9.4|46.1|47.3 |
| motorcycle | 0.0|0.3|0.6 |
| bus | 2.0|27.5|36.5 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.4|10.1|0.9 |
| cycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.7|24.7|32.7 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 96.0|37.7|0.3 |
| cycle | 0.8|6.4|0.7 |
| car | 2.3|21.8|16.7 |
| motorcycle | 0.0|2.7|1.1 |
| bus | 0.4|24.3|58.0 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 88.5|23.7|0.2 |
| cycle | 3.5|8.8|1.9 |
| car | 7.2|49.5|32.3 |
| motorcycle | 0.1|1.6|1.0 |
| bus | 0.3|10.3|29.8 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 62.2|7.2|3.0 |
| cycle | 0.7|0.9|0.3 |
| car | 22.0|45.1|29.9 |
| motorcycle | 1.3|2.9|3.8 |
| bus | 13.3|39.2|32.7 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.1|23.1|0.1 |
| cycle | 4.0|9.0|2.4 |
| car | 0.6|2.9|2.8 |
| motorcycle | 9.9|30.1|29.2 |
| bus | 1.3|34.8|65.4 |
